### 2013-06-25 cws/emnlp_cws/discussion.tex
adding EMNLP13 paper directory; added two reference papers in cws_literature

\section{Discussion}

In this section we talked about detailed consistency analysis and maybe give some examples.
\subsection{Dual decomposition convergence}
Plot the histogram of the number of iterations it takes to converge, and percentage of optimality.

\subsection{consistency}

give results of the consistency analysis

\subsection{oracle}

Give results of the oracle experiment

\subsection{Error analysis}
Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.

### 2013-06-25 cws/emnlp_cws/dual-decomp.tex
adding EMNLP13 paper directory; added two reference papers in cws_literature

\section{Dual-Decomposition}

Dual decomposition offers a ideal framework for combining these two sources of signals without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{}.  
Give a brief description of DD algorithm, focus on the intuition. See \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL} for a good short introduction example.
Refer users to \cite{Rush:2012:JAIR} for a full tutorial on dual decomp.
The modification to Viterbi decoding is exactly the same as in \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL}. The modification to the beam-search is similar, each time we extend a hypothesis with a new character, depending if the new character is appended to the last word or starting a new word, the corresponding DD penalty is factored into the score for the new hypothesis.

### 2013-06-25 cws/emnlp_cws/introduction.tex
adding EMNLP13 paper directory; added two reference papers in cws_literature

\section{Introduction}

First paragraph talks about why Chinese Word Segmentation is important.

Second paragraph talks about the challenges, specifically ambiguity and unknown words.

Third paragraph: There are two classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, each has their respective advantage and disadvantage: char-based segmenters models the internal structure of word composition better and therefore are more effective at detecting out-of-vocabulary words, however they suffer from inconsistency issues. Word-segmenters are better at memorizing the training word type lexicon, and have better consistency, but not as good at detecting OOV words. An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

Fourth paragraph (maybe consider moving some of this into a related work section and put it at the end): various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.

\cite{Sun:2009:HLT-NAACL} is the most similar in that they also try to directly combine two segmenters -- one char-based and one word-based. But they do it through segmenter bagging, which would require training up 50 or more individual segmenters and poll their results at test time, significantly increases training and testing effort, not practical.
\cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.

\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenter based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It's easy to implement and does not require retraining of existing character and word segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model consistently outperform the word and character baselines by significant margin on all 8 datasets. In particular, it improves OOV recall rates and consistency (yet to be validated pending consistency experiment results). It gives the best reported results to date on 6 out of 8 datasets.

### 2013-06-25 cws/emnlp_cws/models.tex
adding EMNLP13 paper directory; added two reference papers in cws_literature

\section{Char-based vs. Word-based Segmenters}

\subsection{Char-based models}
Describe models that treat CWS as a character sequence tagging task (first proposed by \cite{Xue:2003:IJCLCLP}), widely adopted and most commonly used these days.
Give the equation of CRF (see \cite{Tseng:2005:SIGHAN}). Briefly describe the features and point out how some of them can be expected to generalize well to OOV words (e.g. suffix and prefix features).

\subsection{Word-based models}
See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.

\subsection{Relative Strength and Weakness}
Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
 The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.

### 2013-06-25 cws/emnlp_cws/relatedwork.tex
adding EMNLP13 paper directory; added two reference papers in cws_literature

\section{Related Work}
If the Introduction section becomes too long, or we have some space left at the end, we can consider move some of the comparison stuff into this section.

### 2013-06-25 cws/emnlp_cws/conclusion.tex
created a separate dir for emnlp13 paper

\section{Conclusion}

In this paper we presented ... blah blah.
Stress the simplicity and effectiveness of our method.

### 2013-06-25 cws/emnlp_cws/experiment.tex
created a separate dir for emnlp13 paper

\section{Experiments}

Give URL for the Stanford CRF segmenter. The perceptron-based word segmenter is a re-implementation of \cite{Zhang:2007:ACL}.
For development data, we used:
Training: CTB section 1-270  400-931 1001-115;   Dev: CTB section 271-300.

Hyper-parameters tuned on the dev set.
Perceptron: 10 iterations of training. 
CRF: L2-regularization Sigma set to 3.
Dual-decomp: initial step size set to 0.1, 100 iterations.

\subsection{Dataset}
Give description of the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. 
List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

### 2013-06-27 cws/emnlp_cws/abstract.tex
added an abstract draft

\begin{abstract}
There are two dominant approaches to Chinese word segmentation problem: word-based and character-based. They each have their own strengths and weaknesses. 
Word-based approaches are better at capturing longer context dependencies, and achieve higher segmentation consistency, whereas character-based approaches model the internal structures of words and can capture more out-of-vocabulary words. It is an intuitive idea to find methods to combine these approaches. Past efforts in combing word and character-based segmenters involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs. In this paper, we propose an effective joint decoding method using dual decomposition, which does not require any additional training. Our method is simple and easy to implement, and achieves best reported results on 6 out of 7 standard SIGHAN evaluation datasets.
\end{abstract}

### 2013-07-02 cws/emnlp_cws/discussion.tex
writing additions etc

@@
 
-In this section we talked about detailed consistency analysis and maybe give some examples.
+%In this section we talked about detailed consistency analysis and maybe give some examples.
+
 \subsection{Dual decomposition convergence}
@@
 
-\subsection{consistency}
+\subsection{Consistency}
 
-give results of the consistency analysis
+\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance.
+Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent results on 6 out of 7 datasets.
 
-\subsection{oracle}
+Consistency Results, Sighan 2003:
 
-Give results of the oracle experiment
+as crf
+0.0428091404101
+as pct
+0.0441475626702
+as dd
+0.042168035925
+cityu crf
+0.0946373294134
+cityu pct
+0.10025983369
+cityu dd
+0.0867128300158
+ctb crf
+0.174004652166
+ctb pct
+0.18632727645
+ctb dd
+0.165767655651
+pku crf
+0.0423983535204
+pku pct
+0.0543269973345
+pku dd
+0.045000565176
+
+Consistency Results, Sighan 2005:
+
+as crf
+0.0718479895225
+as pct
+0.0681887138263
+as dd
+0.0624082516494
+cityu crf
+0.0660880615807
+cityu pct
+0.0742624297
+cityu dd
+0.0627869624389
+msr crf
+0.0755273737469
+msr pct
+0.064051889613
+msr dd
+0.0558050161967
+pku crf
+0.0892311495453
+pku pct
+0.0998921318846
+pku dd
+0.0868198134889
+
+\subsection{Oracle}
+
+Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results.
+
+To do so, we combine our two baselines with the gold-standard segmentation.
+Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard.
+We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.
+
+The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
+
+% this is here to know what each column means in the output below
+%=== TOTAL INSERTIONS:	75
+%=== TOTAL DELETIONS:	84
+%=== TOTAL SUBSTITUTIONS:	783
+%=== TOTAL NCHANGE:	942
+%=== TOTAL TRUE WORD COUNT:	11989
+%=== TOTAL TEST WORD COUNT:	11980
+%=== TOTAL TRUE WORDS RECALL:	0.928
+%=== TOTAL TEST WORDS PRECISION:	0.928
+%=== F MEASURE:	0.928
+%=== OOV Rate:	0.022
+%=== OOV Recall Rate:	0.810
+%=== IV Recall Rate:	0.930
+Scoring Oracle Output, Sighan 2003
+for as
+	sighan2003/as.oracle	75	84	783	942	11989	11980	0.928	0.928	0.928	0.022	0.810	0.930
+for cityu
+	sighan2003/cityu.oracle	402	333	2364	3099	35087	35156	0.923	0.921	0.922	0.071	0.824	0.931
+for ctb
+	sighan2003/ctb.oracle	920	1005	4490	6415	39921	39836	0.862	0.864	0.863	0.181	0.773	0.882
+for pku
+	sighan2003/pku.oracle	186	187	1593	1966	17194	17193	0.896	0.897	0.897	0.069	0.834	0.901
+
+Scoring Oracle Output, Sighan 2003
+for as
+	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
+for cityu
+	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
+for msr // currently broken
+	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
+for pku
+	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896
 
 \subsection{Error analysis}
+% this makes sense, i will do this tomorrow
 Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.

### 2013-07-02 cws/emnlp_cws/experiment.tex
cleaned up results section, added a table to experiment section
writing additions etc

@@
 
-Give URL for the Stanford CRF segmenter. The perceptron-based word segmenter is a re-implementation of \cite{Zhang:2007:ACL}.
+In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.
+For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml}
+For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}.
+
+% question: what is the relationship between this dev data and that used in sighan2003/2005?
 For development data, we used:
@@
 List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.
+
+\begin{table}
+\centering
+\begin{small}
+\begin{tabular}{ l | l | c | c | c | c | c   }
+%\cline{2-10}
+%\hline
+% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No.
+of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
+\hline
+    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
+\hline
+\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
+& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
+& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
+& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
+\hline
+\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
+& PU  &  - & - & - & - & 6.9 \\
+& CU  & - & - & - & - & 7.1  \\
+%\hline
+%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
+%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
+%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
+%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\
+
+\end{tabular} 
+\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
+\end{small}
+\end{table}

### 2013-07-02 cws/emnlp_cws/introduction.tex
cleaned up results section, added a table to experiment section
writing additions etc

@@
 
-First paragraph talks about why Chinese Word Segmentation is important.
+%First paragraph talks about why Chinese Word Segmentation is important.
+Chinese text is written without delimiters between words; as a result, Chinese word segmentation (CWS) is an essential foundational step for many tasks in Chinese natural language processing.
+As demonstrated by [cite, cite, cite - Pichuan, what else?], the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, [and...].
 
-Second paragraph talks about the challenges, specifically ambiguity and unknown words.
+%Second paragraph talks about the challenges, specifically ambiguity and unknown words.
+State-of-the-art performance in CWS is high, with F-scores in the upper 90s. %say this in a nicer way?
+Still, challenges remain. Unknown words, also known as out-of-vocabulary (\textsc{oov}) words, lead to difficulties for word- or dictionary-based approaches.
+Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able"). % from Gao acl 2003
 
-Third paragraph: There are two classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, each has their respective advantage and disadvantage: char-based segmenters models the internal structure of word composition better and therefore are more effective at detecting out-of-vocabulary words, however they suffer from inconsistency issues.
-Word-segmenters are better at memorizing the training word type lexicon, and have better consistency, but not as good at detecting OOV words.
-An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct.
+%Third paragraph: 
+There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages.
+Character-based segmenters better model the internal compositional structure of words and are therefore more effective at detecting out-of-vocabulary words; however, they suffer from relative inconsistency.
+% problematic - our experiments show this isn't really true, the CRF is more consistent 6/8 times
+Word-based segmenters are better at reproducing the words of the training lexicon and have a higher consistency, but are not as good at detecting \textsc{oov} words.
+Word-based models have the additional advantage that they tend to capture information from significantly larger contextual spans.
+% too detailed?
+%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
+
+%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct.
 Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.
 
-Fourth paragraph (maybe consider moving some of this into a related work section and put it at the end): various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
-
-\cite{Sun:2009:HLT-NAACL} is the most similar in that they also try to directly combine two segmenters -- one char-based and one word-based.
-But they do it through segmenter bagging, which would require training up 50 or more individual segmenters and poll their results at test time, significantly increases training and testing effort, not practical.
-\cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.
-
-\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
-In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.
-
-In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenter based on dual decomposition.
+In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition.
 This method has strong optimality guarantees and works very well empirically.
-It's easy to implement and does not require retraining of existing character and word segmenters.
-Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model consistently outperform the word and character baselines by significant margin on all 8 datasets.
-In particular, it improves OOV recall rates and consistency (yet to be validated pending consistency experiment results).
-It gives the best reported results to date on 6 out of 8 datasets.
+It is easy to implement and does not require retraining of existing character- and word-based segmenters.
+Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin on all 8 datasets.
+% wait, aren't we showing results for only 7?
+In particular, it improves \textsc{oov} recall rates and consistency, % this is now validated
+and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-02 cws/emnlp_cws/relatedwork.tex
writing additions etc

@@
 \section{Related Work}
-If the Introduction section becomes too long, or we have some space left at the end, we can consider move some of the comparison stuff into this section.
+
+\subsection{Character-based Models}
+In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word.
+Conditional random fields (CRFs) are often used for this purpose (cite, cite, cite).
+In a CRF segmentation model, the probability of a label sequence is given by this equation:
+
+%[add eq here]
+% add defs of all the variables
+
+Common linguistic features include character n-grams and morphological suffix/prefix features.
+Since these features capture information about the compositional properties of characters, they are likely to generalize well to unknown words.
+
+\subsection{Word-based Models}
+
+See \cite{Sun:2010:COLING} for a good description.
+We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features.
+Point out how some of these features basically directly capture the training lexicon.
+%
+%\subsection{Relative Strength and Weakness}
+%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).
+(NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section).
+But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
+% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV.
+Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
+%
+
+\subsection{Mixing Models} various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
+
+\cite{Sun:2009:HLT-NAACL} is the most similar in that they also try to directly combine two segmenters -- one char-based and one word-based.
+But they do it through segmenter bagging, which would require training up 50 or more individual segmenters and poll their results at test time, significantly increases training and testing effort, not practical.
+\cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.
+
+\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
+In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.

### 2013-07-03 cws/emnlp_cws/discussion.tex
a few updates

@@
 Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.
+
+some errors where DD picks the wrong model:
+gold: 有 亭台樓閣 流水
+CRF: 亭台 樓閣  <-- DD
+PCT: 亭台樓閣
+
+gold: 大規模 海陸空 聯合 軍演   
+CRF: 大規模 海 陸空 聯合 軍演   <-- DD
+PCT: 大規模 海陸空 聯合 軍演
+
+gold: 在 李鄭屋邨 附近
+CRF: 在 李鄭屋邨 附近
+PCT: 在 李鄭屋 邨 附近   <-- DD
+
+gold: 麥 父 笑說
+CRF:  麥 父 笑說
+PCT: 麥父 笑說    <-- DD
+
+gold: 天氣 熱 時 冷氣 大 開     
+CRF: 天氣 熱 時 冷氣 大 開     
+PCT: 天氣 熱時 冷氣 大 開     <-- DD

### 2013-07-03 cws/emnlp_cws/relatedwork.tex
a few updates

@@
 
-See \cite{Sun:2010:COLING} for a good description.
+Initially word-based segmentation approaches employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}, contemporary approaches use machine learning techniques to solve an argmax problem of the form:
+
+% add eq
+
+%See \cite{Sun:2010:COLING} for a good description.
 We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features.
@@
 
-\subsection{Mixing Models} various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
+\subsection{Mixing Models} Since the two types of models described above have different strengths and make different kinds of errors, various mixing approaches have been proposed to combine them \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
+
+\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
+In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.
 
@@
 \cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.
-
-\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
-In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.

### 2013-07-04 cws/emnlp_cws/conclusion.tex
more updates

@@
 
-In this paper we presented ... blah blah.
-Stress the simplicity and effectiveness of our method.
+In this paper we presented a straightforward approach to Chinese word segmentation using dual decomposition for system combination.
+We demonstrated that this method allows for joint decoding of existing CWS systems that performs better than either system alone on standard datasets for the task, and
+
+We also demonstrated that our joint system produces more consistent segmentations than our baselines, a property that has potentially important downstream impacts for many Chinese NLP tasks.
+It remains to

### 2013-07-04 cws/emnlp_cws/discussion.tex
more updates

@@
 as crf
-0.0428091404101
+0.037814800237
 as pct
-0.0441475626702
+0.038997075095
 as dd
-0.042168035925
+0.0372484903836
 cityu crf
-0.0946373294134
+0.0923886605473
 cityu pct
-0.10025983369
+0.097496193366
 cityu dd
-0.0867128300158
+0.0843064189868
 ctb crf
-0.174004652166
+0.170532711404
 ctb pct
-0.18632727645
+0.181993909505
 ctb dd
-0.165767655651
+0.161722439818
 pku crf
-0.0423983535204
+0.0429803512049
 pku pct
-0.0543269973345
+0.0552572297562
 pku dd
-0.045000565176
+0.0460509973844
 
@@
 as crf
-0.0718479895225
+0.0635314146511
 as pct
-0.0681887138263
+0.0603263902622
 as dd
-0.0624082516494
+0.055097582491
 cityu crf
-0.0660880615807
+0.0649537861096
 cityu pct
-0.0742624297
+0.0730776631941
 cityu dd
-0.0627869624389
+0.0618197636595
 msr crf
-0.0755273737469
+0.073782773985
 msr pct
-0.064051889613
+0.0628241148726
 msr dd
-0.0558050161967
+0.054883418641
 pku crf
-0.0892311495453
+0.0888607888366
 pku pct
-0.0998921318846
+0.0996634383663
 pku dd
-0.0868198134889
+0.086635535204
 
@@
 
-Scoring Oracle Output, Sighan 2003
+Scoring Oracle Output, Sighan 2005
 for as

### 2013-07-04 cws/emnlp_cws/experiment.tex
more updates

--- 2013-06-25 cws/emnlp_cws/experiment.tex
@@
 
-Give URL for the Stanford CRF segmenter. The perceptron-based word segmenter is a re-implementation of \cite{Zhang:2007:ACL}.
-For development data, we used:
-Training: CTB section 1-270  400-931 1001-115;   Dev: CTB section 271-300.
+In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.
 
-Hyper-parameters tuned on the dev set.
-Perceptron: 10 iterations of training. 
-CRF: L2-regularization Sigma set to 3.
-Dual-decomp: initial step size set to 0.1, 100 iterations.
+For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
+and sigma set to 3.
 
-\subsection{Dataset}
-Give description of the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. 
-List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.
+For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.
+
+For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.
+
+% question: what is the relationship between this dev data and that used in sighan2003/2005?
+We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.
+
+\subsection{Datasets}
+Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets.
+[Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]
+
+%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.
+
+%
+%\begin{table}
+%\centering
+%\begin{small}
+%\begin{tabular}{ l | l | c | c | c | c | c   }
+%%\cline{2-10}
+%%\hline
+%% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No.
+of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
+%\hline
+%    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
+%\hline
+%\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
+%& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
+%& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
+%& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
+%\hline
+%\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
+%& PU  &  - & - & - & - & 6.9 \\
+%& CU  & - & - & - & - & 7.1  \\
+%%\hline
+%%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
+%%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
+%%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
+%%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\
+%
+%\end{tabular} 
+%\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
+%\end{small}
+%\end{table}

### 2013-07-04 cws/emnlp_cws/introduction.tex
more updates

@@
 Still, challenges remain. Unknown words, also known as out-of-vocabulary (\textsc{oov}) words, lead to difficulties for word- or dictionary-based approaches.
-Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able"). % from Gao acl 2003
+Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able") \cite{Gao:2003:ACL}.
 
@@
 There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages.
-Character-based segmenters better model the internal compositional structure of words and are therefore more effective at detecting out-of-vocabulary words; however, they suffer from relative inconsistency.
-% problematic - our experiments show this isn't really true, the CRF is more consistent 6/8 times
-Word-based segmenters are better at reproducing the words of the training lexicon and have a higher consistency, but are not as good at detecting \textsc{oov} words.
-Word-based models have the additional advantage that they tend to capture information from significantly larger contextual spans.
+\cite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
+Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
+
 % too detailed?
@@
 It is easy to implement and does not require retraining of existing character- and word-based segmenters.
-Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin on all 8 datasets.
-% wait, aren't we showing results for only 7?
-In particular, it improves \textsc{oov} recall rates and consistency, % this is now validated
+Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin.
+In particular, it improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
 and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-04 cws/emnlp_cws/models.tex
more updates

@@
-\section{Char-based vs. Word-based Segmenters}
+\section{Models for CWS}
 
-\subsection{Char-based models}
-Describe models that treat CWS as a character sequence tagging task (first proposed by \cite{Xue:2003:IJCLCLP}), widely adopted and most commonly used these days.
-Give the equation of CRF (see \cite{Tseng:2005:SIGHAN}). Briefly describe the features and point out how some of them can be expected to generalize well to OOV words (e.g. suffix and prefix features).
+In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.
 
-\subsection{Word-based models}
-See \cite{Sun:2010:COLING} for a good description.
+\subsection{Character-based Models}
+In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word.
+Conditional random fields (CRFs) are often used for this purpose (cite, cite, cite).
+In a CRF segmentation model, the probability of a label sequence is given by this equation:
+
+%[add eq here]
+% add defs of all the variables
+
+Common linguistic features include character n-grams and morphological suffix/prefix features.
+Since these features capture information about the compositional properties of characters, they are likely to generalize well to unknown words.
+
+\subsection{Word-based Models}
+
+Initially word-based segmentation approaches employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}, contemporary approaches use machine learning techniques to solve an argmax problem of the form:
+
+% add eq
+
+The most successful such system reported to date is \cite{Zhang:2007:ACL}'s Perceptron-based model, which uses a search-based discriminative decoder to solve the ... %MQ add here?
+
+%See \cite{Sun:2010:COLING} for a good description.
 We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features.
 Point out how some of these features basically directly capture the training lexicon.
-
-\subsection{Relative Strength and Weakness}
-Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).
+%
+%\subsection{Relative Strength and Weakness}
+%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).
 (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section).
 But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
- The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV.
+% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV.
 Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
+%
+
+\subsection{Mixing Models} Since the two types of models described above have different strengths and make different kinds of errors, various mixing approaches have been proposed to combine them \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
+
+\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both incorporate a character-based Maxent local classifier model with a language model that captures more word-level context.
+In order to bring in a bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various forms of conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm with a complexity of $O(T^3)$.
+
+\cite{Sun:2009:HLT-NAACL} presented a latent-variable model which obtains good performance, but it is very complicated to implement and difficult to train. 
+\cite{Sun:2009:HLT-NAACL} use a method most similar to this work in that they also directly combine two segmenters -- one char-based and one word-based.
+However, they do it through segmenter bagging, which requires training 50 or more individual segmenters and polling their results at test time.
+
+These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

### 2013-07-05 cws/emnlp_cws/abstract.tex
a bunch of cleanups and additional writing

@@
 \begin{abstract}
-There are two dominant approaches to Chinese word segmentation problem: word-based and character-based. They each have their own strengths and weaknesses. 
-Word-based approaches are better at capturing longer context dependencies, and achieve higher segmentation consistency, whereas character-based approaches model the internal structures of words and can capture more out-of-vocabulary words.
+There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths and weaknesses.
+Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs.
+In this paper, we propose an effective and consistent joint decoding method using dual decomposition, which does not require any additional training.
+Our method is simple and easy to implement, and achieves the best reported results to date on 6 out of 7 standard SIGHAN evaluation datasets.
+\end{abstract}
+
+%%
+%Word-based approaches are better at capturing longer context dependencies, and achieve higher segmentation consistency, whereas character-based approaches model the internal structures of words and can capture more out-of-vocabulary words.
 It is an intuitive idea to find methods to combine these approaches.
-Past efforts in combing word and character-based segmenters involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs.
-In this paper, we propose an effective joint decoding method using dual decomposition, which does not require any additional training.
-Our method is simple and easy to implement, and achieves best reported results on 6 out of 7 standard SIGHAN evaluation datasets.
-\end{abstract}

### 2013-07-05 cws/emnlp_cws/conclusion.tex
a bunch of cleanups and additional writing

--- 2013-06-25 cws/emnlp_cws/conclusion.tex
@@
 
-In this paper we presented ... blah blah.
-Stress the simplicity and effectiveness of our method.
+In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination.
+We demonstrated that this method allows for joint decoding of existing CWS systems that performs better than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
+
+We also demonstrated that our joint system produces more consistent segmentations than our baselines.
+This property that has potentially important downstream impacts for many Chinese NLP tasks, though it remains to test this empirically.
+
+Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used.
+This suggests its potential for broader applicability in real-world settings than existing approaches to combining character-based and word-based models for Chinese word segmentation.

### 2013-07-05 cws/emnlp_cws/discussion.tex
a bunch of cleanups and additional writing

@@
 %In this section we talked about detailed consistency analysis and maybe give some examples.
+
+On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.
 
@@
 \cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance.
-Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent results on 6 out of 7 datasets.
+Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent segmentations (lowest conditional entropy) on 6 out of 7 datasets.
 
@@
 0.086635535204
-
-\subsection{Oracle}
-
-Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results.
-
-To do so, we combine our two baselines with the gold-standard segmentation.
+%
+%\subsection{Oracle}
+%
+%Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results. 
+%
+%To do so, we combine our two baselines with the gold-standard segmentation.
 Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard.
 We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.
-
-The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
-
-% this is here to know what each column means in the output below
-%=== TOTAL INSERTIONS:	75
-%=== TOTAL DELETIONS:	84
-%=== TOTAL SUBSTITUTIONS:	783
-%=== TOTAL NCHANGE:	942
-%=== TOTAL TRUE WORD COUNT:	11989
-%=== TOTAL TEST WORD COUNT:	11980
-%=== TOTAL TRUE WORDS RECALL:	0.928
-%=== TOTAL TEST WORDS PRECISION:	0.928
-%=== F MEASURE:	0.928
-%=== OOV Rate:	0.022
-%=== OOV Recall Rate:	0.810
-%=== IV Recall Rate:	0.930
-Scoring Oracle Output, Sighan 2003
-for as
-	sighan2003/as.oracle	75	84	783	942	11989	11980	0.928	0.928	0.928	0.022	0.810	0.930
-for cityu
-	sighan2003/cityu.oracle	402	333	2364	3099	35087	35156	0.923	0.921	0.922	0.071	0.824	0.931
-for ctb
-	sighan2003/ctb.oracle	920	1005	4490	6415	39921	39836	0.862	0.864	0.863	0.181	0.773	0.882
-for pku
-	sighan2003/pku.oracle	186	187	1593	1966	17194	17193	0.896	0.897	0.897	0.069	0.834	0.901
-
-Scoring Oracle Output, Sighan 2005
-for as
-	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
-for cityu
-	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
-for msr // currently broken
-	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
-for pku
-	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896
+%
+%The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
+%
+%% this is here to know what each column means in the output below
+%%=== TOTAL INSERTIONS:	75
+%%=== TOTAL DELETIONS:	84
+%%=== TOTAL SUBSTITUTIONS:	783
+%%=== TOTAL NCHANGE:	942
+%%=== TOTAL TRUE WORD COUNT:	11989
+%%=== TOTAL TEST WORD COUNT:	11980
+%%=== TOTAL TRUE WORDS RECALL:	0.928
+%%=== TOTAL TEST WORDS PRECISION:	0.928
+%%=== F MEASURE:	0.928
+%%=== OOV Rate:	0.022
+%%=== OOV Recall Rate:	0.810
+%%=== IV Recall Rate:	0.930
+%Scoring Oracle Output, Sighan 2003
+%for as
+%	sighan2003/as.oracle	79	88	173	340	11989	11980	0.978	0.979	0.979	0.071	0.940	0.981
+%for cityu
+%	sighan2003/cityu.oracle	402	333	893	1628	35087	35156	0.965	0.963	0.964	0.073	0.823	0.976
+%for ctb
+%	sighan2003/ctb.oracle	929	1014	2504	4447	39921	39836	0.912	0.914	0.913	0.230	0.822	0.939
+%for pku
+%	sighan2003/pku.oracle	189	190	392	771	17194	17193	0.966	0.966	0.966	0.138	0.925	0.973
+%Scoring Oracle Output, Sighan 2003
+%for as
+%	sighan2005/as.oracle	1876	748	2542	5166	122610	123739	0.973	0.964	0.969	0.099	0.890	0.982
+%for cityu
+%	sighan2005/cityu.oracle	577	371	1136	2084	40936	41142	0.963	0.958	0.961	0.075	0.839	0.973
+%for msr // currently broken
+%	sighan2005/msr.oracle	81	107	165	353	10987	10961	0.975	0.978	0.976	0.065	0.934	0.978
+%for pku
+%	sighan2005/pku.oracle	803	1664	2505	4972	104372	103511	0.960	0.968	0.964	0.124	0.924	0.965
+%
 
 \subsection{Error analysis}
-% this makes sense, i will do this tomorrow
-Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.
 
-some errors where DD picks the wrong model:
-gold: 有 亭台樓閣 流水
-CRF: 亭台 樓閣  <-- DD
-PCT: 亭台樓閣
+Since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems.
+In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."
 
-gold: 大規模 海陸空 聯合 軍演   
-CRF: 大規模 海 陸空 聯合 軍演   <-- DD
-PCT: 大規模 海陸空 聯合 軍演
+%some errors where DD picks the wrong model:
+%gold: 有 亭台樓閣 流水
+%CRF: 亭台 樓閣  <-- DD
+%PCT: 亭台樓閣
+\begin{tabbing}
 
-gold: 在 李鄭屋邨 附近
-CRF: 在 李鄭屋邨 附近
-PCT: 在 李鄭屋 邨 附近   <-- DD
+\ \ \ \ \= \emph{English}\ \ \ \ \= Large-scale sea, land, and air \\ 
+\> \> joint military exercises\\
+\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
 
-gold: 麥 父 笑說
-CRF:  麥 父 笑說
-PCT: 麥父 笑說    <-- DD
+\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
 
-gold: 天氣 熱 時 冷氣 大 開     
-CRF: 天氣 熱 時 冷氣 大 開     
-PCT: 天氣 熱時 冷氣 大 開     <-- DD
+\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
+
+\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
+\end{tabbing}
+
+Nevertheless, in many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone.
+The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.
+
+\begin{tabbing}
+\ \ \ \ \= \emph{English}\ \ \ \ \= Tian Yage's creations \\
+\> \emph{Gold} \>   田雅各 / 的 / 创作 \\
+\> \emph{CRF} \>  田雅各的 / 创作 \\
+\> \emph{PCPT} \>  田雅 / 各 / 的 / 创作 \\
+\> \emph{DD} \>  田雅各 / 的 / 创作 \\
+\end{tabbing}
+
+A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or polling-of-experts model could not, since joint decoding allows the sharing of information at decoding time.
+In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
+
+\begin{tabbing}
+\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy a bit of snack food, ... \\
+\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
+\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
+\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
+\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
+\end{tabbing}
+We found more than 400 such surprisingly accurate instances in our dual decomposition output.
+%
+%gold: 在 李鄭屋邨 附近
+%CRF: 在 李鄭屋邨 附近
+%PCT: 在 李鄭屋 邨 附近   <-- DD
+%
+%gold: 麥 父 笑說
+%CRF:  麥 父 笑說
+%PCT: 麥父 笑說    <-- DD
+%
+%gold: 天氣 熱 時 冷氣 大 開     
+%CRF: 天氣 熱 時 冷氣 大 開     
+%PCT: 天氣 熱時 冷氣 大 開     <-- DD

### 2013-07-05 cws/emnlp_cws/experiment.tex
a bunch of cleanups and additional writing

@@
 \subsection{Datasets}
-Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets.
-[Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]
+We run our experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets.
+Specifically, we use the standard training and test splits for the 2003 Academia Sinica (AS), Peking University (PU), and City University of Hong Kong (CU) datasets as well as the 2005 AS, PU, CU, and Microsoft Research (MSR) datasets.
+We do not use the 2003 Chinese Treebank dataset because...
+[why exactly?]
 

### 2013-07-05 cws/emnlp_cws/abstract.tex
abstract, results table changes

@@
 \begin{abstract}
-There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths and weaknesses.
-Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs.
-In this paper, we propose an effective and consistent joint decoding method using dual decomposition, which does not require any additional training.
-Our method is simple and easy to implement, and achieves the best reported results to date on 6 out of 7 standard SIGHAN evaluation datasets.
+There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths.
+Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however,
+Past efforts have not provided a practical technique to allow mainstream adoption.
+We propose a method that effectively combines the strength of both segmentation schemes using an efficient dual-decomposition algorithm for joint inference.
+Our method is simple and easy to implement.
+Experiments on SIGHAN 2003 and 2005 evaluation datasets show that our method achieves the best reported results to date on 6 out of 7 datasets.
 \end{abstract}

### 2013-07-05 cws/emnlp_cws/discussion.tex
abstract, results table changes

@@
 
-Consistency Results, Sighan 2003:
-
-as crf
-0.037814800237
-as pct
-0.038997075095
-as dd
-0.0372484903836
-cityu crf
-0.0923886605473
-cityu pct
-0.097496193366
-cityu dd
-0.0843064189868
-ctb crf
-0.170532711404
-ctb pct
-0.181993909505
-ctb dd
-0.161722439818
-pku crf
-0.0429803512049
-pku pct
-0.0552572297562
-pku dd
-0.0460509973844
-
-Consistency Results, Sighan 2005:
-
-as crf
-0.0635314146511
-as pct
-0.0603263902622
-as dd
-0.055097582491
-cityu crf
-0.0649537861096
-cityu pct
-0.0730776631941
-cityu dd
-0.0618197636595
-msr crf
-0.073782773985
-msr pct
-0.0628241148726
-msr dd
-0.054883418641
-pku crf
-0.0888607888366
-pku pct
-0.0996634383663
-pku dd
-0.086635535204
 %
@@
 %PCT: 亭台樓閣
+\begin{small}
 \begin{tabbing}
-
-\ \ \ \ \= \emph{English}\ \ \ \ \= Large-scale sea, land, and air \\ 
-\> \> joint military exercises\\
+\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
+\> \> joint / military exercises\\
 \> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
@@
 \end{tabbing}
-
+\end{small}
 Nevertheless, in many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone.
@@
 
+\begin{small}
 \begin{tabbing}
-\ \ \ \ \= \emph{English}\ \ \ \ \= Tian Yage's creations \\
+\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Tian Yage / 's / creations \\
 \> \emph{Gold} \>   田雅各 / 的 / 创作 \\
@@
 \end{tabbing}
+\end{small}
 
@@
 In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
-
+\begin{small}
 \begin{tabbing}
-\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy a bit of snack food, ... \\
+\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
 \> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
@@
 \end{tabbing}
+\end{small}
 We found more than 400 such surprisingly accurate instances in our dual decomposition output.

### 2013-07-05 cws/emnlp_cws/introduction.tex
a bunch of cleanups and additional writing
abstract, results table changes

@@
 There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages.
-\cite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
+\newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
 Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
-
 % too detailed?
 %Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.
-
 %An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct.

### 2013-07-06 cws/emnlp_cws/abstract.tex
major revision, mostly complete except for DD description

@@
 There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths.
-Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however,
-Past efforts have not provided a practical technique to allow mainstream adoption.
+Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts have not provided a practical technique to allow mainstream adoption.
 We propose a method that effectively combines the strength of both segmentation schemes using an efficient dual-decomposition algorithm for joint inference.

### 2013-07-06 cws/emnlp_cws/discussion.tex
major revision, mostly complete except for DD description

@@
-\section{Discussion}
-
-%In this section we talked about detailed consistency analysis and maybe give some examples.
+\section{Discussion and Error Analysis}
 
 On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.
+On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
+In 77.4\% of the cases, DD converged in the first iteration. For the remaining cases, the number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.
 
-\subsection{Dual decomposition convergence}
-Plot the histogram of the number of iterations it takes to converge, and percentage of optimality.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{histogram.png}
+\caption{No. of iterations till DD convergence histogram.}
+\label{fig:histo}
+\end{center}
+\end{figure}
 
-\subsection{Consistency}
-
-\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance.
-Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent segmentations (lowest conditional entropy) on 6 out of 7 datasets.
-
-%
-%\subsection{Oracle}
-%
-%Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results. 
-%
-%To do so, we combine our two baselines with the gold-standard segmentation.
-Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard.
-We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.
-%
-%The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
-%
-%% this is here to know what each column means in the output below
-%%=== TOTAL INSERTIONS:	75
-%%=== TOTAL DELETIONS:	84
-%%=== TOTAL SUBSTITUTIONS:	783
-%%=== TOTAL NCHANGE:	942
-%%=== TOTAL TRUE WORD COUNT:	11989
-%%=== TOTAL TEST WORD COUNT:	11980
-%%=== TOTAL TRUE WORDS RECALL:	0.928
-%%=== TOTAL TEST WORDS PRECISION:	0.928
-%%=== F MEASURE:	0.928
-%%=== OOV Rate:	0.022
-%%=== OOV Recall Rate:	0.810
-%%=== IV Recall Rate:	0.930
-%Scoring Oracle Output, Sighan 2003
-%for as
-%	sighan2003/as.oracle	79	88	173	340	11989	11980	0.978	0.979	0.979	0.071	0.940	0.981
-%for cityu
-%	sighan2003/cityu.oracle	402	333	893	1628	35087	35156	0.965	0.963	0.964	0.073	0.823	0.976
-%for ctb
-%	sighan2003/ctb.oracle	929	1014	2504	4447	39921	39836	0.912	0.914	0.913	0.230	0.822	0.939
-%for pku
-%	sighan2003/pku.oracle	189	190	392	771	17194	17193	0.966	0.966	0.966	0.138	0.925	0.973
-%Scoring Oracle Output, Sighan 2003
-%for as
-%	sighan2005/as.oracle	1876	748	2542	5166	122610	123739	0.973	0.964	0.969	0.099	0.890	0.982
-%for cityu
-%	sighan2005/cityu.oracle	577	371	1136	2084	40936	41142	0.963	0.958	0.961	0.075	0.839	0.973
-%for msr // currently broken
-%	sighan2005/msr.oracle	81	107	165	353	10987	10961	0.975	0.978	0.976	0.065	0.934	0.978
-%for pku
-%	sighan2005/pku.oracle	803	1664	2505	4972	104372	103511	0.960	0.968	0.964	0.124	0.924	0.965
-%
-
-\subsection{Error analysis}
+\paragraph{Error analysis}
 

### 2013-07-06 cws/emnlp_cws/experiment.tex
major revision, mostly complete except for DD description

--- 2013-07-04 cws/emnlp_cws/experiment.tex
@@
 
-In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.
+\begin{table*}[t]
+\centering
+\begin{small}
+\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
+%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
+\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{AS} &  \multicolumn{5}{c}{PU} \\
+\hline
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
+Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064  &  94.6 &	95.3 & 94.9  &   77.8   & 0.089    \\
+Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
+Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
+%\cline{2-9}
+\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{CU} &  \multicolumn{5}{c}{MSR}  \\
+\hline
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
+Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
+Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7  & 0.073 &  97.0 &  97.2 & 97.1  & 74.6 & 0.063  \\
+Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
+\end{tabular} 
+\caption{Results on SIGHAN 2005 datasets. {R$_{\mathrm{oov}}$}  denotes OOV recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency. }\label{tbl:results}
+\end{small}
+\end{table*}
 
-For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
-and sigma set to 3.
-
-For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.
-
-For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.
-
-% question: what is the relationship between this dev data and that used in sighan2003/2005?
-We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.
-
-\subsection{Datasets}
-Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets.
-[Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]
-
+We conduct experiments  on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual-decomposition algorithm.
+We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
+We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
+The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual-decomposition is run to max iteration of 100 with initial step size of 0.1.
+Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}.
+They have shown that increased segmentation consistency is correlated with better machine translation performance.
+The consistency measure calculates the entropy of segmentation variations -- the lower the score the better.
 %List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
major revision, mostly complete except for DD description

@@
 Chinese text is written without delimiters between words; as a result, Chinese word segmentation (CWS) is an essential foundational step for many tasks in Chinese natural language processing.
-As demonstrated by [cite, cite, cite - Pichuan, what else?], the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, [and...].
+As demonstrated by \cite{Shi:2007:IJCAI,Bai:2008:IJCNLP,Chang:2008:ACL,Kummerfeld:2013:ACL}, the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, POS tagging and parsing.
 

### 2013-07-06 cws/emnlp_cws/models.tex
a bunch of cleanups and additional writing
major revision, mostly complete except for DD description

--- 2013-06-25 cws/emnlp_cws/models.tex
@@
-\section{Char-based vs. Word-based Segmenters}
+\section{Models for CWS}
 
-\subsection{Char-based models}
-Describe models that treat CWS as a character sequence tagging task (first proposed by \cite{Xue:2003:IJCLCLP}), widely adopted and most commonly used these days.
-Give the equation of CRF (see \cite{Tseng:2005:SIGHAN}). Briefly describe the features and point out how some of them can be expected to generalize well to OOV words (e.g. suffix and prefix features).
+In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.
 
-\subsection{Word-based models}
-See \cite{Sun:2010:COLING} for a good description.
-We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features.
-Point out how some of these features basically directly capture the training lexicon.
+\subsection{Character-based Models}
+In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word.
+Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}.
+In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
+\begin{align*}
+P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp^{ \vec\theta \vec{f}(x, y_{t}, y_{t+1}) } }}
+\end{align*}
+\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features.
+These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.
+But the Markov assumption in CRF limits the context of such features, it is difficult to capture long-range word features in this model. 
+%, which is important for admitting efficient inference, restricts the CRF to very local context features.
+A first-order CRF can only reason about character boundary decisions of current and neighboring positions.
+%It is therefore difficult to directly model words of greater length.
+Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.
 
-\subsection{Relative Strength and Weakness}
-Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).
-(NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section).
-But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
- The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV.
-Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
+\subsection{Word-based Models}
+Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
+Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}.
+More recent success was reported by  \newcite{Zhang:2007:ACL}, who used a linear discriminative model to score candidate word lists.
+More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that $F(\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{x}) }$.
+Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}.
+Searching through the entire  search space $\mathrm{GEN}(\mathbf{x})$ is intractable even with a local model.
+A beam-search algorithm is therefore employed.
+The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypothesis by either appending the new character to the last word in the beam, or start a new word at current position.
+
+\subsection{Combine Models with Dual-decomposition} 
+Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
+These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.
+
+Dual decomposition offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
+DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
+
+Give a brief description of DD algorithm, focus on the intuition. See \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL} for a good short introduction example.
+Refer users to \cite{Rush:2012:JAIR} for a full tutorial on dual decomp.
+The modification to Viterbi decoding is exactly the same as in \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL}.
+The modification to the beam-search is similar, each time we extend a hypothesis with a new character, depending if the new character is appended to the last word or starting a new word, the corresponding DD penalty is factored into the score for the new hypothesis.

### 2013-07-06 cws/emnlp_cws/conclusion.tex
model desscription section completed

@@
 In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination.
-We demonstrated that this method allows for joint decoding of existing CWS systems that performs better than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
-
-We also demonstrated that our joint system produces more consistent segmentations than our baselines.
-This property that has potentially important downstream impacts for many Chinese NLP tasks, though it remains to test this empirically.
-
+We demonstrated that this method allows for joint decoding of existing CWS systems that are more accurate and consistent than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
 Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used.

### 2013-07-06 cws/emnlp_cws/models.tex
model desscription section completed

@@
 More recent success was reported by  \newcite{Zhang:2007:ACL}, who used a linear discriminative model to score candidate word lists.
-More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that $F(\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{x}) }$.
-Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}.
+More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
+\begin{align*}
+F(\mathbf{y}|\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{\mathbf{y}}) }
+\end{align*}
+\noindent Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}.
 Searching through the entire  search space $\mathrm{GEN}(\mathbf{x})$ is intractable even with a local model.
@@
 The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypothesis by either appending the new character to the last word in the beam, or start a new word at current position.
+
+\begin{algorithm}[!ht]
+\begin{footnotesize}
+\caption{DD inference algorithm, modified Viterbi and BeamSearch.}
+\begin{algorithmic}
+\STATE $\forall i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} \colon \; \forall k \in \{0,1\} \colon u_{i}(k) = 0$
+\FOR{$t \leftarrow 1$  \textbf{to} $T$}
+\STATE   $\mathbf{y^{c*}} = \argmaxb \; P(\mathbf{y^\textit{c}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c})}$ 
+\STATE   $\mathbf{y^{w*}} = \argmax \; F(\mathbf{y^\textit{w}} | \mathbf{x}) -  \sum\limits_{i\in |\mathbf{x}|}{ u_{i}(y_j^\textit{w})}$
+\IF{ $\mathbf{y^{c*}} =  \mathbf{y^{w*}}$ }
+\RETURN $\left(\mathbf{y^{\textit{c}*}},\mathbf{y^{\textit{w}*}}\right)$
+\ENDIF
+\FORALL{$i \in \{1\; \mathrm{to} \; |\mathbf{x}|\} $}
+\STATE  $\forall k \in \{0,1\}: u_i(k)=u_i(k) + \alpha_t (2k-1)(y_i^{w*}-y_i^{c*})$ 
+\ENDFOR
+\ENDFOR
+\RETURN $\left(\mathbf{y^{c*}},\mathbf{y^{w*}}\right)$
+ \\\hrulefill
+\STATE Viterbi: 
+\STATE $V_1(1) = 1, V_1(0) = 0$
+\FOR{$i = 2 \; \mathrm{to} \; |\mathbf{x}|$}
+\STATE $\forall k \in \{0,1\}: V_i(k) = \argmaxk P_i(k | k') V_{i-1}{k'} + u_{i}(k)$ 
+\ENDFOR
+ \\\hrulefill
+\STATE BeamSearch:
+\FOR{$i = 1 \; \mathrm{to} \; |\mathbf{x}|$}
+\FOR{ item $v = \{w_0,\cdots,w_j\}$ in $\mathrm{beam}(i)$}
+\STATE append $x_i$ to $w_j$, $\mathrm{score}(v) \stackrel{+}{=}   u_{i}(0)$
+\STATE $v = \{w_0,\cdots,w_j, x_i\}$, $\mathrm{score}(v) \stackrel{+}{=} u_{i}(1)$
+\ENDFOR
+\ENDFOR
+\end{algorithmic}
+\label{algo:DD}
+\end{footnotesize}
+\end{algorithm}
 
@@
 
-Dual decomposition offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
+Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
 DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
 
-Give a brief description of DD algorithm, focus on the intuition. See \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL} for a good short introduction example.
-Refer users to \cite{Rush:2012:JAIR} for a full tutorial on dual decomp.
-The modification to Viterbi decoding is exactly the same as in \cite{Wang:2013:ACL} and \cite{Denero:2011:ACL}.
-The modification to the beam-search is similar, each time we extend a hypothesis with a new character, depending if the new character is appended to the last word or starting a new word, the corresponding DD penalty is factored into the score for the new hypothesis.
+The high-level idea is that jointly model both character-sequence and word information can be difficult, so instead we explore the joint search space at inference time to find an output that the two models are most likely to agree.
+Formally, the objective that DD optimizes is:
+\begin{align*}
+   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
+\end{align*}
+\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.
+
+The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other.
+This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other.
+We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algorithm~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

### 2013-07-06 cws/emnlp_cws/experiment.tex
minor fixes

@@
 We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
-The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual-decomposition is run to max iteration of 100 with initial step size of 0.1.
+The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual-decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1.
 Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}.

### 2013-07-06 cws/emnlp_cws/discussion.tex
minor fixes
everything but stats-sig test results

@@
 
-On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.
+On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
 On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
-In 77.4\% of the cases, DD converged in the first iteration. For the remaining cases, the number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{histogram.png}
-\caption{No. of iterations till DD convergence histogram.}
-\label{fig:histo}
-\end{center}
-\end{figure}
+In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.
 
@@
 
-A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or polling-of-experts model could not, since joint decoding allows the sharing of information at decoding time.
+A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time.
 In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
@@
 We found more than 400 such surprisingly accurate instances in our dual decomposition output.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\columnwidth]{histogram.png}
+\caption{No. of iterations till DD convergence.}
+\label{fig:histo}
+\end{center}
+\end{figure}
+
 %

### 2013-07-06 cws/emnlp_cws/experiment.tex
everything but stats-sig test results

--- 2013-07-05 cws/emnlp_cws/experiment.tex
@@
 
-In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition.
-
-For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml} In this system we use L2 regularization with a value of X %TODO: insert actual value / word this properly
-and sigma set to 3.
-
-For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}, run with 10 iterations of training.
-
-For joint decoding with dual decomposition, we use an initial step size set to 0.1, and run for 100 iterations.
-
-% question: what is the relationship between this dev data and that used in sighan2003/2005?
-We use the same development set employed by \cite{Zhang:2007:ACL}, with Chinese Treebank sections 1-270, 400-931, and 1001-115 used as training data and sections 271-300 used as development data for tuning the hyperparameters of all three systems.
-
-\subsection{Datasets}
-We run our experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets.
-Specifically, we use the standard training and test splits for the 2003 Academia Sinica (AS), Peking University (PU), and City University of Hong Kong (CU) datasets as well as the 2005 AS, PU, CU, and Microsoft Research (MSR) datasets.
-We do not use the 2003 Chinese Treebank dataset because...
-[why exactly?]
-
-%List a table of the corpora names, size of training, testing, etc, similar to \cite{Sun:2010:COLING}.
-
-%
-%\begin{table}
-%\centering
-%\begin{small}
-%\begin{tabular}{ l | l | c | c | c | c | c   }
-%%\cline{2-10}
-%%\hline
-%% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No.
-of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
-%\hline
-%    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
-%\hline
-%\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
-%& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
-%& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
-%& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
-%\hline
-%\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
-%& PU  &  - & - & - & - & 6.9 \\
-%& CU  & - & - & - & - & 7.1  \\
-%%\hline
-%%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
-%%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
-%%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
-%%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\
-%
-%\end{tabular} 
-%\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
-%\end{small}
-%\end{table}
+We conduct experiments  on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm.
+We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
+We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
+The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1.
+Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}.
+They have shown that increased segmentation consistency is correlated with better machine translation performance.
+The consistency measure calculates the entropy of segmentation variations --- the lower the score the better.
+Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
everything but stats-sig test results

@@
 There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages.
-\newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new out-of-vocabulary words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
+\newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
 Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.

### 2013-07-06 cws/emnlp_cws/models.tex
minor fixes
everything but stats-sig test results

@@
 In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
-\begin{align*}
-P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp^{ \vec\theta \vec{f}(x, y_{t}, y_{t+1}) } }}
+\begin{align*}\vspace{-10em}
+P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
+\vspace{-10em}
 \end{align*}
@@
 These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.
-But the Markov assumption in CRF limits the context of such features, it is difficult to capture long-range word features in this model. 
+But the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
 %, which is important for admitting efficient inference, restricts the CRF to very local context features.
@@
 Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. 
-More recent success was reported by  \newcite{Zhang:2007:ACL}, who used a linear discriminative model to score candidate word lists.
-More concretely, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
+ \newcite{Zhang:2007:ACL} reported more recent success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
+ Formally, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
 \begin{align*}
-F(\mathbf{y}|\mathbf{x}) =  \argmax{ \vec\alpha \vec\phi(\mathbf{\mathbf{y}}) }
+F(\mathbf{y}|\mathbf{x}) =  \argmax{ \left( \alpha \cdot \phi(\mathbf{\mathbf{y}}) \right) }
 \end{align*}
-\noindent Feature weights are trained using the average perceptron algorithm \cite{Collins:2002:EMNLP}.
-Searching through the entire  search space $\mathrm{GEN}(\mathbf{x})$ is intractable even with a local model.
+\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model.
 A beam-search algorithm is therefore employed.
-The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypothesis by either appending the new character to the last word in the beam, or start a new word at current position.
+The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or start a new word at current position.
 
@@
 \begin{footnotesize}
-\caption{DD inference algorithm, modified Viterbi and BeamSearch.}
+\caption{DD inference algorithm, modified Viterbi and beam-search.}
 \begin{algorithmic}
@@
  \\\hrulefill
-\STATE BeamSearch:
+\STATE Beam-Search:
 \FOR{$i = 1 \; \mathrm{to} \; |\mathbf{x}|$}
@@
 
-\subsection{Combine Models with Dual-decomposition} 
+\begin{table*}
+\centering
+\begin{small}
+\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
+%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
+\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{AS} &  \multicolumn{5}{c}{PU} \\
+\hline
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
+Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064  &  94.6 &	95.3 & 94.9  &   77.8   & 0.089    \\
+Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
+Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
+%\cline{2-9}
+\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{CU} &  \multicolumn{5}{c}{MSR}  \\
+\hline
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
+Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
+Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7  & 0.073 &  97.0 &  97.2 & 97.1  & 74.6 & 0.063  \\
+Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
+\end{tabular} 
+\caption{Results on SIGHAN 2005 datasets.
+{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency.
+$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively.
+}\label{tbl:results}
+\end{small}
+\end{table*}
+
+\subsection{Combine Models with Dual Decomposition} 
 Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
@@
 
-The high-level idea is that jointly model both character-sequence and word information can be difficult, so instead we explore the joint search space at inference time to find an output that the two models are most likely to agree.
-Formally, the objective that DD optimizes is:
+The idea is that jointly model both character-sequence and word information can be computationally challenging,  instead we could try to find outputs that the two models are most likely to agree on.
+Formally, the objective of DD is:
 \begin{align*}
@@
 This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other.
-We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algorithm~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.
+We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

### 2013-07-06 cws/emnlp_cws/conclusion.tex
grammatical edits mostly

@@
 In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination.
-We demonstrated that this method allows for joint decoding of existing CWS systems that are more accurate and consistent than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
+We demonstrated that this method allows for joint decoding of existing CWS systems that is more accurate and consistent than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
 Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used.

### 2013-07-06 cws/emnlp_cws/discussion.tex
grammatical edits mostly

@@
 A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time.
-In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
+In the following example, both baseline models miss the contextually clear use of the word 点心 (``sweets / snack food") and instead attach 点 to the prior word to produce the otherwise common compound 一点点 (``a little bit"); dual decomposition allows the model to generate the correct segmentation.
 \begin{small}

### 2013-07-06 cws/emnlp_cws/experiment.tex
grammatical edits mostly

@@
 We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm.
-We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
+We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
 We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
 The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1.
-Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}.
-They have shown that increased segmentation consistency is correlated with better machine translation performance.
+Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance.
 The consistency measure calculates the entropy of segmentation variations --- the lower the score the better.

### 2013-07-06 cws/emnlp_cws/models.tex
grammatical edits mostly

@@
 In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word.
-Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}.
+Conditional random fields (CRF) \cite{Lafferty:2001:ICML} are widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}.
 In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
@@
 \end{align*}
-\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features.
+\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding n-gram and morphological suffix/prefix features.
 These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.
-But the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
+However, the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
 %, which is important for admitting efficient inference, restricts the CRF to very local context features.
@@
 \subsection{Word-based Models}
-Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
+Word-based models search through lists of word candidates using scoring functions that directly assign scores to each. 
 Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. 
- \newcite{Zhang:2007:ACL} reported more recent success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
- Formally, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
+More recently, \newcite{Zhang:2007:ACL} reported success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
+ Formally, given input $\mathbf{x}$, their model seeks a segmentation $F(\mathbf{x})$ such that:
 \begin{align*}
@@
 \end{align*}
-\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model.
-A beam-search algorithm is therefore employed.
-The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or start a new word at current position.
+\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model, so a beam-search algorithm is used.
+The search algorithm consumes one character input token at a time, and iterates through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or starting a new word at the current position.
 
@@
 
-\subsection{Combine Models with Dual Decomposition} 
+\subsection{Combining Models with Dual Decomposition} 
 Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
@@
 
-Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
-DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
+Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high costs in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
+DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
 
-The idea is that jointly model both character-sequence and word information can be computationally challenging,  instead we could try to find outputs that the two models are most likely to agree on.
+The idea is that jointly modelling both character-sequence and word information can be computationally challenging, so instead we can try to find outputs that the two models are most likely to agree on.
 Formally, the objective of DD is:
@@
 The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other.
-This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other.
-We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.
+This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other.
+We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitations, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

### 2013-07-06 cws/emnlp_cws/discussion.tex
edits to error analysis

@@
 
-Since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems.
-In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."
+%In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."
 
-%some errors where DD picks the wrong model:
-%gold: 有 亭台樓閣 流水
-%CRF: 亭台 樓閣  <-- DD
-%PCT: 亭台樓閣
-\begin{small}
-\begin{tabbing}
-\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
-\> \> joint / military exercises\\
-\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
-
-\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
-
-\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
-
-\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
-\end{tabbing}
-\end{small}
-Nevertheless, in many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone.
+%%some errors where DD picks the wrong model:
+%%gold: 有 亭台樓閣 流水
+%%CRF: 亭台 樓閣  <-- DD
+%%PCT: 亭台樓閣
+%\begin{small}
+%\begin{tabbing}
+%\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Large-scale / sea, land, and air / \\ 
+%\> \> joint / military exercises\\
+%\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\
+%
+%\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
+%
+%\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\
+%
+%\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
+%\end{tabbing}
+%\end{small}
+In many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone.
 The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.
@@
 
+Finally, since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems.
+
 \begin{figure}

### 2013-07-06 cws/emnlp_cws/models.tex
removed stats-sig descriptions
final edits

@@
 Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
-Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
-Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
+Word-based Perceptron &  95.8 & \textbf{95.0} & \textbf{95.4}  & \textbf{69.5} & 0.060  &  94.1             & 95.5  & 94.8  &  76.7 & 0.099     \\ 
+Dual-decomp      & \textbf{95.9} & 94.9   & \textbf{95.4}  & {67.7} & \textbf{0.055}            & \textbf{94.8} & \textbf{95.7} & \textbf{95.3}  &  \textbf{78.7} & \textbf{0.086}   \\
 %\cline{2-9}
@@
 \multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
-Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
+Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
 Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7                                         & 0.073              &  97.0 &              97.2                & 97.1  & 74.6 & 0.063  \\
-Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
+Dual-decomp                   & \textbf{95.0} & \textbf{94.4}  & \textbf{94.7}  & {75.3} & \textbf{0.062} & \textbf{97.3} &  \textbf{97.4} &  \textbf{97.4}  & \textbf{76.0} & \textbf{0.055}  \\
 \end{tabular} 
@@
 {R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency.
-$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively.
+Best number in each column is highlighted in bold.
+The naming of the datasets are: \emph{AS} --- Academia Sinica, \emph{PU} --- Peking University, \emph{CU} --- City Univeristy, \emph{MSR} ---  Microsoft Research.
+%$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. 
 }\label{tbl:results}

### 2013-07-06 cws/emnlp_cws/discussion.tex
final edits
a bunch of final minor changes

@@
 In many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone.
-The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.
+The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based perceptron, but our method achieves the correct middle ground.
 

### 2013-07-06 cws/emnlp_cws/experiment.tex
removed stats-sig descriptions
a bunch of final minor changes

@@
 We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
-The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1.
+The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}).
 Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance.
 The consistency measure calculates the entropy of segmentation variations --- the lower the score the better.
-Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.
+%Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2013-07-06 cws/emnlp_cws/introduction.tex
a bunch of final minor changes

@@
 %Third paragraph: 
-There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages.
-\newcite{Sun:2010:COLING} details their theoretical distinctions: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
+There are two primary classes of models: character-based, where the foundational units for processing are individual Chinese characters \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING}, and word-based, where the units are full words based on some dictionary or training lexicon \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}.
+\newcite{Sun:2010:COLING} details their respective theoretical strengths: character-based approaches better model the internal compositional structure of words and are therefore more effective at inducing new \textsc{oov} words; word-based approaches are better at reproducing the words of the training lexicon and can capture information from significantly larger contextual spans.
 Prior work has shown performance gains from combining these two types of models to exploit their respective strengths, but such approaches are often complex to implement and computationally expensive.
@@
 Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin.
-In particular, it improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
+In particular, out approach improves \textsc{oov} recall rates and segmentation consistency, % this is now validated
 and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-06 cws/emnlp_cws/models.tex
a bunch of final minor changes

--- 2013-07-06 cws/emnlp_cws/models.tex
@@
 
-In this section, we describe the character-based and word-based models we use as baselines, and review existing approaches to combine these models.
+In this section, we describe the character-based and word-based models we use as baselines, review existing approaches to combination, and describe our algorithm for joint decoding with dual decomposition.
 
@@
 In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word.
-Conditional random fields (CRF) \cite{Lafferty:2001:ICML} are widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}.
+Conditional random fields (CRF) \cite{Lafferty:2001:ICML} have been widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}.
 In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
@@
 \end{align*}
-\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding n-gram and morphological suffix/prefix features.
+\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding character n-gram and morphological suffix/prefix features.
 These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.
@@
 Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high costs in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}).
-DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
+DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}, bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.
 

### 2013-07-06 cws/emnlp_cws/abstract.tex
edited in chris's comments, submitted version

@@
 \begin{abstract}
-There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths.
+There are two dominant approaches to Chinese word segmentation: word-based and character-based models, each with respective strengths.
 Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts have not provided a practical technique to allow mainstream adoption.

### 2013-07-06 cws/emnlp_cws/discussion.tex
edited in chris's comments, submitted version

@@
 On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
-On the SIGHAN 2005 test set, over 99.1\% cases the DD algorithm converged within 100 iterations which gives optimality guarantee. 
+On the SIGHAN 2005 test set, in over 99.1\% cases the DD algorithm converged within 100 iterations which gives an optimality guarantee. 
 In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.
@@
 
-\begin{small}
+\begin{footnotesize}
 \begin{tabbing}
@@
 \end{tabbing}
-\end{small}
+\end{footnotesize}
 
@@
 In the following example, both baseline models miss the contextually clear use of the word 点心 (``sweets / snack food") and instead attach 点 to the prior word to produce the otherwise common compound 一点点 (``a little bit"); dual decomposition allows the model to generate the correct segmentation.
-\begin{small}
+\begin{footnotesize}
 \begin{tabbing}
@@
 \end{tabbing}
-\end{small}
+\end{footnotesize}\vspace{-3mm}
 We found more than 400 such surprisingly accurate instances in our dual decomposition output.
 
-Finally, since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems.
+Finally, since dual decomposition is a method of joint decoding, it is still liable to reproduce errors made by the constituent systems.
 

### 2013-07-06 cws/emnlp_cws/models.tex
edited in chris's comments, submitted version

--- 2013-07-06 cws/emnlp_cws/models.tex
@@
 %\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
-\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{AS} &  \multicolumn{5}{c}{PU} \\
+\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{Academia Sinica} &  \multicolumn{5}{c}{Peking Univ.} \\
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\
 Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
-Word-based Perceptron &  95.8 & 95.0 & 95.4  & 69.5 & 0.060  &  94.1 & 95.5  & 94.8  &  76.7 & 0.099     \\ 
-Dual-decomp      & 95.9 & 94.9   & {95.4}  & {67.7} & 0.055 & 94.8 & {95.7} & {95.3}  &  {78.7} & 0.086   \\
+Word-based Perceptron &  95.8 & \textbf{95.0} & \textbf{95.4}  & \textbf{69.5} & 0.060  &  94.1             & 95.5  & 94.8  &  76.7 & 0.099     \\ 
+Dual-decomp      & \textbf{95.9} & 94.9   & \textbf{95.4}  & {67.7} & \textbf{0.055}            & \textbf{94.8} & \textbf{95.7} & \textbf{95.3}  &  \textbf{78.7} & \textbf{0.086}   \\
 %\cline{2-9}
-\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{CU} &  \multicolumn{5}{c}{MSR}  \\
+\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{City Univ. of Hong Kong} &  \multicolumn{5}{c}{Microsoft Research}  \\
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C$_{\mathrm{onst}}$} \\
-Char-based CRF    & 94.7 & 94.0 & 94.3  & {76.1}  & 0.065 & 96.4 &   96.6 & 96.5  & 71.3 & 0.074 \\
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\
+Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
 Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7                                         & 0.073              &  97.0 &              97.2                & 97.1  & 74.6 & 0.063  \\
-Dual-decomp  & {95.0} & 94.4  & {94.7}  & {75.3} & 0.062 &  {97.3} &  {97.4} &  {97.4}  & {76.0} & 0.055  \\
+Dual-decomp                   & \textbf{95.0} & \textbf{94.4}  & \textbf{94.7}  & {75.3} & \textbf{0.062} & \textbf{97.3} &  \textbf{97.4} &  \textbf{97.4}  & \textbf{76.0} & \textbf{0.055}  \\
 \end{tabular} 
 \caption{Results on SIGHAN 2005 datasets.
-{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and C$_{\mathrm{onst}}$ denotes segmentation consistency.
-$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively.
+\textit{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and \textit{Consist} denotes segmentation consistency.
+Best number in each column is highlighted in bold.
+%$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. 
 }\label{tbl:results}

### 2013-08-17 cws/response.txt
adding author's response

Thank you for your thoughtful feedback and helpful suggestions. We
look forward to revising our paper in light of your comments.
Please allow us to give some detailed answers to Reviewer #2's comments.

> though it's not clear if the improvements over the baselines and previous state-of-the-art systems are significant
Statistical significance tests using the paired bootstrap resampling method with 1000 iterations (Efron and Tibshirani, 1993) shows that our DD algorithm is significantly better than the character-based CRF basedline in F1 score in 4 out of 4 cases on SIGHAN 2005 dataset at 95% confidence level, and is significantly better than the word-based perceptron baseline in 3 out of 4 cases (except for AS) at the same confidence level.
We will report full details in the final writeup upon acceptance.

> I realise space is at a premium but I think the introduction and sections 2.1 and 2.2 could easily be compressed to make room.
Great suggestion! We will make our notations more consistent and provide more details of the DD algorithm.

> They provide no analysis of why Sun 10 outperforms their model on the CU set. It would be interesting to see some discussion regarding this point. 
Sun 2010 did not make their code or system outputs available, therefore it is difficult to obtain a fine-grained comparison of our algorithm with his on the CU set. 
However, there are two high-level differences we observe: 1) Both our chracter-based and word-based baseline systems give numbers that are significantly lower (by more than 1% in F1) on this dataset than Sun 2010; although DD algorithm improves upon both baselines, it is bounded by the quality of the underlying systems. 
2) We did not perform any dataset-specific post-processing in any of our systems since the main focus of the paper is to demonstrate the merits of combining word and character-based systems using the DD algorithm. 
Various reports from the SIGHAN participants have suggested that tricks like number and date normalization post-processing can lead to significant improvements for particular datasets, which could be a factor for the performance difference.

> It converges given one test set but this doesn't constitute a guarantee. It's not a proof.
We apologize for the confusion, but the optimality guarantee that we were referring to is with respect to the constrained-optimization problem of the joint objective (Rush et al. ACL 2010 outlined a proof for the guarantee); we were not stating that the DD algorithm is guaranteed to give the optimal results for the respective task. We will clarify it in the final writeup.

### 2013-08-17 cws/response.txt
minor copyedits

@@
 > I realise space is at a premium but I think the introduction and sections 2.1 and 2.2 could easily be compressed to make room.
-Great suggestion! We will make our notations more consistent and provide more details of the DD algorithm.
+Great suggestion! We will make our notation more consistent and provide further details on the DD algorithm.
 
 > They provide no analysis of why Sun 10 outperforms their model on the CU set. It would be interesting to see some discussion regarding this point. 
-Sun 2010 did not make their code or system outputs available, therefore it is difficult to obtain a fine-grained comparison of our algorithm with his on the CU set. 
+Sun 2010 did not make their code or system outputs available, so it is difficult to obtain a fine-grained comparison of our algorithm with his on the CU set. 
 However, there are two high-level differences we observe: 1) Both our chracter-based and word-based baseline systems give numbers that are significantly lower (by more than 1% in F1) on this dataset than Sun 2010; although DD algorithm improves upon both baselines, it is bounded by the quality of the underlying systems.
 2) We did not perform any dataset-specific post-processing in any of our systems since the main focus of the paper is to demonstrate the merits of combining word and character-based systems using the DD algorithm.
-Various reports from the SIGHAN participants have suggested that tricks like number and date normalization post-processing can lead to significant improvements for particular datasets, which could be a factor for the performance difference.
+Various reports from the SIGHAN participants have suggested that tricks like number and date normalization post-processing can lead to significant improvements for particular datasets, which could be a factor in the performance difference.
 
@@
 We apologize for the confusion, but the optimality guarantee that we were referring to is with respect to the constrained-optimization problem of the joint objective (Rush et al.
-ACL 2010 outlined a proof for the guarantee); we were not stating that the DD algorithm is guaranteed to give the optimal results for the respective task.
-We will clarify it in the final writeup.
+ACL 2010 outlined a proof for the guarantee); we were not stating that the DD algorithm is guaranteed to give optimal results for the given task.
+We will clarify this in the final writeup.

### 2014-03-12 cws/emnlp_cws/discussion.tex
copyediting updates

@@
 On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
-On the SIGHAN 2005 test set, in over 99.1\% cases the DD algorithm converged within 100 iterations which gives an optimality guarantee. 
+On the SIGHAN 2005 test set, in over 99.1\% of cases the DD algorithm converged within 100 iterations, which gives an optimality guarantee. 
 In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.
@@
 \begin{tabbing}
-\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
+\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
 \> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\

### 2014-03-12 cws/emnlp_cws/experiment.tex
copyediting updates

@@
 We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
-We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development.
-The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}).
-Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance.
+
+We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training and sections 400-931 for development in hyper-parameter setting; for all results given in tables, the models are trained and evaluated on the standard train/test split for the given dataset.
+The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; the perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}).
+
+Beyond standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance.
 The consistency measure calculates the entropy of segmentation variations --- the lower the score the better.
+We also report out-of-vocabulary recall (R$_{\mathrm{oov}}$) as an estimation of the model's generalizability to previously unseen words.
+
 %Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2014-03-12 cws/emnlp_cws/models.tex
copyediting updates

@@
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
 Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
@@
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\
+\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
 Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
@@
 \end{tabular} 
-\caption{Results on SIGHAN 2005 datasets.
-\textit{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and \textit{Consist} denotes segmentation consistency.
-Best number in each column is highlighted in bold.
+\caption{Results on SIGHAN 2005 datasets. \textit{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and \textit{C} denotes segmentation consistency. Best number in each column is highlighted in bold.
 %$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. 
@@
 This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other.
-We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitations, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.
+We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for the DD algorithm in Algo.~\ref{algo:DD}.\footnote{See \newcite{Rush:2012:JAIR} for a full introduction to DD.}

### 2014-03-13 cws/emnlp_cws/models.tex
expanded DD model description

@@
 \STATE   $\mathbf{y^{c*}} = \argmaxb \; P(\mathbf{y^\textit{c}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c})}$ 
-\STATE   $\mathbf{y^{w*}} = \argmax \; F(\mathbf{y^\textit{w}} | \mathbf{x}) -  \sum\limits_{i\in |\mathbf{x}|}{ u_{i}(y_j^\textit{w})}$
+\STATE   $\mathbf{y^{w*}} = \argmax \; F(\mathbf{y^\textit{w}} | \mathbf{x}) -  \sum\limits_{j\in |\mathbf{x}|}{ u_{j}(y_j^\textit{w})}$
 \IF{ $\mathbf{y^{c*}} =  \mathbf{y^{w*}}$ }
@@
 Formally, the objective of DD is:
-\begin{align*}
-   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
-\end{align*}
-\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.
+\begin{align}
+   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  s.t. \; \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
+\end{align}
+\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF, $\mathbf{y^\textit{w}}$ is the output of word-based perceptron, 
+and the agreements  are expressed as constraints. \textit{s.t.} is a shorthand for ``such that''.
 
-The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other.
+Solving this constrained optimization problem directly is difficult. 
+Instead, we take the Lagrangian relaxation of this term as:
+\begin{align}
+& L\left(\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}, \mathbf{U}\right) =  \\ 
+& P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c}-y_i^\textit{w})}  \nonumber \label{eq:sub}
+\end{align}
+\noindent where $ \mathbf{U}$ is the set of Lagrangian multipliers that consists of a multiplier $u_i$ at each word position $i$.
+
+We can rewrite the original objective with the Lagrangian relaxation as:
+\begin{align}
+   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}} \min_{\mathbf{U}} \; L\left(\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}, \mathbf{U}\right)
+\end{align}
+
+We can then form the dual of this problem by taking the $\min$ outside of the $\max$, which is an upper bound on the original problem.  
+The dual form can then be decomposed into two sub-components (the two $\max$ problems in Eq.~\ref{eq:sub}), each of which is local with respect to the set of Lagrangian multipliers:
+\begin{align}
+\min_{\mathbf{U}}  \Biggl( & \max_{y^\textit{c}} \left[  P(\mathbf{y^\textit{c}} | \mathbf{x})  + \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c}})  \right] \\ \nonumber
+ +  &  \max_{y^\textit{w}}   \left[  F(\mathbf{y^\textit{w}} | \mathbf{x})  - \sum\limits_{j\in |\mathbf{x}|}{u_{j}(y_j^\textit{w})}  \right] \Biggr)
+\end{align}
+This method is called dual decomposition (DD) \cite{Rush:2010:EMNLP}.
+Similar to previous work \cite{Rush:2012:JAIR}, we solve this DD problem by iteratively updating the sub-gradient as depicted in Algorithm~\ref{algo:DD}.\footnote{See \newcite{Rush:2012:JAIR} for a full introduction to DD.}
+In each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other.
 This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other.
-We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for the DD algorithm in Algo.~\ref{algo:DD}.\footnote{See \newcite{Rush:2012:JAIR} for a full introduction to DD.}
+We also give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron in Algorithm~\ref{algo:DD}.
+$T$ is the maximum number of iterations before early stopping, and $\alpha_t$ is the learning rate at time $t$.
+We adopt a learning rate update rule from \newcite{Koo:2010:EMNLP} where $\alpha_t$ is defined as ${\frac{1}{N}}$, where $N$ is the number of times we observed a consecutive dual value increase from iteration $1$ to $t$.

### 2014-03-13 cws/emnlp_cws/models.tex
expanded title box

@@
 \begin{footnotesize}
-\caption{DD inference algorithm, modified Viterbi and beam-search.}
+\caption{Dual decomposition inference algorithm, and modified Viterbi and beam-search algorithms.}
 \begin{algorithmic}
@@
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
+\multicolumn{1}{c|}{}   & \multicolumn{1}{c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c|}{C}  & \multicolumn{1}{c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
 Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
@@
 %\cline{2-9}
+\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{} &  \multicolumn{5}{c}{} \\
 \multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{City Univ. of Hong Kong} &  \multicolumn{5}{c}{Microsoft Research}  \\
 \hline
-\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
+\multicolumn{1}{c|}{}   & \multicolumn{1}{c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c|}{C}  & \multicolumn{1}{c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\
 Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
@@
 & L\left(\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}, \mathbf{U}\right) =  \\ 
-& P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c}-y_i^\textit{w})}  \nonumber \label{eq:sub}
+& P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) +  \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c}-y_i^\textit{w})}  \nonumber
 \end{align}
@@
 The dual form can then be decomposed into two sub-components (the two $\max$ problems in Eq.~\ref{eq:sub}), each of which is local with respect to the set of Lagrangian multipliers:
-\begin{align}
+\begin{align}\label{eq:sub}
 \min_{\mathbf{U}}  \Biggl( & \max_{y^\textit{c}} \left[  P(\mathbf{y^\textit{c}} | \mathbf{x})  + \sum\limits_{i\in |\mathbf{x}|}{u_{i}(y_i^\textit{c}})  \right] \\ \nonumber
